MCC Models

### 2019-04-26 papers/full_paper/manuscript.Rmd
first draft paper si

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
    email         : "bohn@stanford.edu"
  - name          : "Michael Henry Tessler"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "1"

@@

author_note: |
  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. We thank Jacqueline Quirke, Sabina Zacco and especially Megan Merrick for help with the data collection.

@@

All analysis were run in R [@R-base]. GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4]. Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl]. The flat prior model had the same structure as the pragmatics model but used a uniform prior over objects. The prior only model predicted choice based on the prior probability for each object alone. Note that the proportions that informed the prior distribution in the pragmatics and prior only model were measured when participants chose between two objects in experiment 2. In experiment 3, however, three objects were involved. For each object we used the proportion measured in experiment 2 as the prior probability. This approach spread out the absolute probability mass but conserved the relative relation between objects. Bayes Factors for model comparisons are based on marginal likelihoods of each model given the data. The corresponding model code can be found in the associated online repository.

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
    email         : "bohn@stanford.edu"
  - name          : "Michael Henry Tessler"
    affiliation   : "3"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

@@

author_note: |
  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund. We thank Jacqueline Quirke and Sabina Zacco for help with the data collection.

@@

All analysis were run in R [@R-base]. GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4]. Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl]. The flat prior model had the same structure as the pragmatics model but used a uniform prior over objects. The prior only model predicted choice based on the prior probability for each object alone. Bayes Factors for model comparisons are based on marginal likelihoods of each model given the data. The corresponding model code can be found in the associated online repository.
